\section{WORK EXPERIENCE}
  \resumeSubHeadingListStart
    \resumeSubheading{Open Source - Flyte}{04/2024 -- Present}
    {Open Source Developer}{Remote}
      \resumeItemListStart
        \resumeItem{Contribute to the Flyte project, a machine learning and data processing platform primarily written in Golang and Python, with a codebase of over 1,000,000 lines.}
        \resumeItem{Developed the interface for remote execution in Flytekit, improving usability in Jupyter notebooks.}
        \resumeItem{Enabled unsafe typing in Flytekit, facilitating easier migration of existing codebases by allowing developers to bypass type checking.}
        \resumeItem{Fixed the usage of the Any type in Flytekit, allowing the correct use of Any type via the command line with the Click package.}
      \resumeItemListEnd
    
    \resumeSubheading
    {Appier}{06/2024 -- 08/2024}
    {AI Research Scientist Intern}{Taiwan}
    \resumeItemListStart
      \resumeItem{Enhanced machine learning algorithms in a recommendation system using Diffusion Models to address data inefficiency and imbalance, reducing performance drop by 25\%.}
      \resumeItem{Analyzed experimental results to derive key insights and contributed to academic paper writing for the research team.}
    \resumeItemListEnd

    \resumeSubheading
      {Taiwan Semiconductor Manufacturing Company(TSMC)}{06/2023 -- 07/2023}
      {Machine Learning Research Engineer Intern}{Taiwan}
      \resumeItemListStart
        \resumeItem{Designed and developed an innovative pairwise Style Transfer model for super-resolution images (3M pixels per image), resulting in a 50\% reduction in error rates.}
        \resumeItem{Optimized the data pipeline with Python MPI for image extraction and processing, achieving a 75\% reduction in processing time.}
        \resumeItem{Implemented TensorFlow distributed computing across 2 nodes with 4 A100 GPUs each, boosting training efficiency by 5 times.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd